\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{Assessing economic inequality with tax data - Switzerland from 1945 to 2010}

### 2014-06-23 paper/subdocuments/results.Rnw
new figures for normal/special and minor fixes

par(mfrow=c(1,3))
g10 <- reldist(y=bd.2010.ind$inc, yo=bd.2003.ind$inc,
               smooth=0.4, ci=FALSE,
               yolabs=seq(-1,3,by=0.5),
               ylim=c(0.5,5.0),
               bar=TRUE, quiet=FALSE,
               xlab="Proportion of 2002 Distribution")
title(main=paste("Overall realtive density"))
abline(h=1,lty=2)
g1A <- reldist(y=bd.2010.ind$inc, yo=bd.2003.ind$inc,
               show="effect",
               bar=TRUE, quiet=FALSE,
               ylim=c(0.5,5.0), ylab="",
               smooth=0.4, ci=FALSE,
               yolabs=seq(-1,3,by=0.5),
               xlab="Proportion of 2002 Distribution")
title(main=paste("Effect of Median shift"))
abline(h=1,lty=2)
gA0 <- reldist(y=bd.2010.ind$inc, yo=bd.2003.ind$inc,
               smooth=0.4, ci=FALSE,
               show="residual",
               bar=TRUE, quiet=FALSE,
               ylim=c(0.5,5.0), ylab="",
               yolabs=seq(-1,3,by=0.5),
               xlab="Proportion of 2002 Distribution")
title(main=paste("Effect of different shape"))
abline(h=1,lty=2)
par(mfrow=c(1,1))
@

@@

The FTA stopped to publicly report data for special cases after tax period 1993/94. 
For more recent periods however we can compare data from the 
BRUELHARTPROJEKT (wie nennen wir das?) to the FTA normal cases, as these data are 
identical but the BRÜLHART data include special cases. 
We will have a look at both, the 1993/94 period as the last period where both 
numbers were reported as well as 2009 where we compare data from the same source 
but using differnt data sheets.

%ABBILDUNGEN ZUM VERGLEICH NORMAL-/SONDERFÄLLE
<<specialcases9394, echo=FALSE,warning=FALSE>>=
library(dplyr, quietly=TRUE, warn.conflicts = FALSE)
library(ggplot2)
#library(reldist)
normal <- read.csv("../../data/ginis_und_perzentile_normal.csv",sep="\t")
#normal <- normal %.% select(-G_reink, -G_taxed, -ppop0, -G_steink0)
pooled <- read.csv("../../data/ginis_und_perzentile_beides.csv",sep="\t")
#special <- read.csv("data/ginis_und_perzentile_sonder.csv",segep="\t")
normal$case <- "normal case"
#special$case <- "special case"
pooled$case <- "pooled, normal and special cases"
d<-rbind(normal,pooled)
d<-d %.% 
  filter(kanton=="CH",steuerperiode==1993.5)

@@

#steuerpflichtige estv / stpf bruelhart
#1- (2762419 / 3268548)
@

<<specialcases09, echo=FALSE,warning=FALSE>>=
library(foreign)
library(ggplot2)
#library(reldist)
normal <- filter(read.csv("../../data/ginis_und_perzentile_normal.csv",sep="\t"),kanton=="CH",steuerperiode==2009)
start <- which(names(normal)=="p1")
end <- which(names(normal)=="p99")
percentile <- c(1,5,10,20,25,30,40,50,60,70,75,80,90,95,99)
normal <- data.frame(t(normal[1,start:end]),percentile)
names(normal)[1]=c("inc")

#bruelhart data
pooled <- filter(read.dta("../../data/data_Schweiz.dta"), Veranlagungsperiode==2009, Einheit=="Total")
start <- which(names(pooled)=="p1")
p95 <- which(names(pooled)=="p95")
end <- which(names(pooled)=="p99")
pooled <- data.frame(t(pooled[1,c(start:p95,end)]),percentile)
names(pooled)[1]=c("inc")
pooled$inc<-pooled$inc/1000 #adjust scale
normal$case <- "normal case"
pooled$case <- "pooled, normal and special cases"
percentiles <- rbind(normal,pooled)
ggplot(percentiles, aes(x=percentile,y=inc,group=case,colour=case))+
	geom_line()+theme_bw()+
	scale_colour_grey()+
	xlab("Percentile")+ylab("taxable income")+
	ggtitle("Taxable incomes of normal and special cases 2009")+
  theme(legend.justification=c(0,1),legend.position=c(0, 1))

#plot relative distribution
rel <- data.frame(pooled$inc,normal$inc,pooled$percentile)
rel$change <- rel$pooled.inc/rel$normal.inc
ggplot(rel, aes(x=pooled.percentile,y=change))+
	geom_line()+theme_bw()+
	geom_line(linetype="dashed",aes(y=1),size=2)+
	scale_colour_grey()+
	xlab("Percentile")+ylab("taxable income")+
	ggtitle("Taxable incomes of normal versus special cases 2009")

#steuerpflichtige estv / stpf bruelhart
#1- (3422210 / 3689063)
@

@@

As we can see from figure~\ref{fig:specialcases93942} and \ref{fig:specialcases092}, special cases differ strongly 
from normal cases within the low and top percentiles. Within the tax period 1993/94 the fifth percentile of 
normal cases is 15.8\% higher than the fifth percentile of the combines data while the 95\% percentile of 
normal cases is even 0.7\% lower if one leaves out special cases. This indicates special cases are very 
different from normal cases as the share of special cases is only 15.5\%.\footnote{1993/94 there were 2.76 
million tax units defined as being normal cases compared to 0.51 million special cases.}
In 2009 the situation has the same pattern. The fifth percentile of normal cases has 11\% higher taxable 
income compared to data where special cases are included. The five percent top incomes are 4.9\% higher 
within all cases compared to normal cases only. The share of special cases however decreased 
to 7.2\%.\footnote{2009: 3.42 million normal cases, 0.27 million special cases}

@@

par(mfrow=c(1,3))
g10 <- reldist(y=estv2010.total.ind$inc, yo=habe10$inc_habe,
               smooth=0.4, ci=FALSE,
               yolabs=seq(-1,3,by=0.5),
               ylim=c(0.5,5.0),
               bar=TRUE, quiet=FALSE,
               xlab="Proportion of HBS Distribution")
title(main=paste("Overall realtive density"))
abline(h=1,lty=2)
g1A <- reldist(y=estv2010.total.ind$inc, yo=habe10$inc_habe,
               show="effect",
               bar=TRUE, quiet=FALSE,
               ylim=c(0.5,5.0), ylab="",
               smooth=0.4, ci=FALSE,
               yolabs=seq(-1,3,by=0.5),
               xlab="Proportion of HBS Distribution")
title(main=paste("Effect of Median shift"))
abline(h=1,lty=2)
gA0 <- reldist(y=estv2010.total.ind$inc, yo=habe10$inc_habe,
               smooth=0.4, ci=FALSE,
               show="residual",
               bar=TRUE, quiet=FALSE,
               ylim=c(0.5,5.0), ylab="",
               yolabs=seq(-1,3,by=0.5),
               xlab="Proportion of HBS Distribution")
title(main=paste("Effect of different shape"))
abline(h=1,lty=2)
par(mfrow=c(1,1))

@@

par(mfrow=c(1,3))
g10 <- reldist(y=estv2010.married.ind$inc, yo=habe10.married$inc_habe,
               smooth=0.4, ci=FALSE,
               yolabs=seq(-1,3,by=0.5),
               ylim=c(0.5,5.0),
               bar=TRUE, quiet=FALSE,
               xlab="Proportion of HBS Distribution")
title(main=paste("Overall realtive density"))
abline(h=1,lty=2)
g1A <- reldist(y=estv2010.married.ind$inc, yo=habe10.married$inc_habe,
               show="effect",
               bar=TRUE, quiet=FALSE,
               ylim=c(0.5,5.0), ylab="",
               smooth=0.4, ci=FALSE,
               yolabs=seq(-1,3,by=0.5),
               xlab="Proportion of HBS Distribution")
title(main=paste("Effect of Median shift"))
abline(h=1,lty=2)
gA0 <- reldist(y=estv2010.married.ind$inc, yo=habe10.married$inc_habe,
               smooth=0.4, ci=FALSE,
               show="residual",
               bar=TRUE, quiet=FALSE,
               ylim=c(0.5,5.0), ylab="",
               yolabs=seq(-1,3,by=0.5),
               xlab="Proportion of HBS Distribution")
title(main=paste("Effect of different shape"))
abline(h=1,lty=2)
par(mfrow=c(1,1))

@@

par(mfrow=c(1,3))
g10 <- reldist(y=estv2010.unmarried.ind$inc, yo=habe10.unmarried$inc_habe,
               smooth=0.4, ci=FALSE,
               yolabs=seq(-1,3,by=0.5),
               ylim=c(0.5,5.0),
               bar=TRUE, quiet=FALSE,
               xlab="Proportion of HBS Distribution")
title(main=paste("Overall realtive density"))
abline(h=1,lty=2)
g1A <- reldist(y=estv2010.unmarried.ind$inc, yo=habe10.unmarried$inc_habe,
               show="effect",
               bar=TRUE, quiet=FALSE,
               ylim=c(0.5,5.0), ylab="",
               smooth=0.4, ci=FALSE,
               yolabs=seq(-1,3,by=0.5),
               xlab="Proportion of HBS Distribution")
title(main=paste("Effect of Median shift"))
abline(h=1,lty=2)
gA0 <- reldist(y=estv2010.unmarried.ind$inc, yo=habe10.unmarried$inc_habe,
               smooth=0.4, ci=FALSE,
               show="residual",
               bar=TRUE, quiet=FALSE,
               ylim=c(0.5,5.0), ylab="",
               yolabs=seq(-1,3,by=0.5),
               xlab="Proportion of HBS Distribution")
title(main=paste("Effect of different shape"))
abline(h=1,lty=2)
par(mfrow=c(1,1))
@

>>>>

par(mfrow=c(1,3))
g10 <- reldist(y=bd.2010.ind$inc, yo=bd.2003.ind$inc,
               smooth=0.4, ci=FALSE,
               yolabs=seq(-1,3,by=0.5),
               ylim=c(0.5,5.0),
               bar=TRUE, quiet=FALSE,
               xlab="Proportion of 2002 Distribution")
title(main=paste("Overall relative density"))
abline(h=1,lty=2)
g1A <- reldist(y=bd.2010.ind$inc, yo=bd.2003.ind$inc,
               show="effect",
               bar=TRUE, quiet=FALSE,
               ylim=c(0.5,5.0), ylab="",
               smooth=0.4, ci=FALSE,
               yolabs=seq(-1,3,by=0.5),
               xlab="Proportion of 2002 Distribution")
title(main=paste("Effect of Median shift"))
abline(h=1,lty=2)
gA0 <- reldist(y=bd.2010.ind$inc, yo=bd.2003.ind$inc,
               smooth=0.4, ci=FALSE,
               show="residual",
               bar=TRUE, quiet=FALSE,
               ylim=c(0.5,5.0), ylab="",
               yolabs=seq(-1,3,by=0.5),
               xlab="Proportion of 2002 Distribution")
title(main=paste("Effect of different shape"))
abline(h=1,lty=2)
par(mfrow=c(1,1))
@

@@

The FTA stopped to publicly report data for special cases after tax period 1993/94. 
For more recent periods however we can compare already calculated percentiles provided by the FTA which are based on both special and normal cases to normal cases alone.
We will have a look at both, the 1993/94 period as the last period where both 
numbers were reported as well as 2010 where we compare data from the same source (FTA)
but based on different reporting (aggregated data vs. percentiles).

%ABBILDUNGEN ZUM VERGLEICH NORMAL-/SONDERFÄLLE
<<specialcases9394, echo=FALSE,warning=FALSE>>=
library(dplyr, quietly=TRUE, warn.conflicts = FALSE)
library(ggplot2)
#library(reldist)
normal <- read.csv("../../data/ginis_und_perzentile_normal.csv",sep="\t")
normal <- select(normal, -G_reink,-G_taxed,-ppop0,-G_steink0)
#normal <- normal %.% select(-G_reink, -G_taxed, -ppop0, -G_steink0)
pooled <- read.csv("../../data/ginis_und_perzentile_beides.csv",sep="\t")
#special <- read.csv("data/ginis_und_perzentile_sonder.csv",segep="\t")
normal$case <- "normal case"
#special$case <- "special case"
pooled$case <- "pooled, normal and special cases"
d<-rbind(normal,pooled)
d<-d %.% 
  filter(kanton=="CH",steuerperiode==1993.5)

@@

#steuerpflichtige estv / stpf bruelhart
#1- (2762419 / 3268548)

# imputing pseudo-individual data to use reldist
# we cut at the 5th and 95th percentile because it is unclear what values to use to extrapolate
ival<-na.omit(normal$inc[-1])
perval<-normal$percentile[-1]
normal_i<-unlist(sapply(2:length(ival),function(i){
  len=(perval[i]-perval[i-1])*100
  seq(ival[i-1],ival[i],length.out=len)
}))

ival<-na.omit(pooled$inc)
perval<-pooled$percentile[-1]
pooled_i<-unlist(sapply(2:length(ival),function(i){
  len=(perval[i]-perval[i-1])*100
  seq(ival[i-1],ival[i],length.out=len)
}))

density1 <- density(normal_i)
plot(x = (density1$x), y = density1$y, type = "l",
     xlab = "taxable income", ylab = "density"
     #axes = FALSE,
     #xlim = c(-50, 200),
     #ylim=c(0,0.0116031)
     )
title(main="normal cases vs pooled, normal and special cases 1993/94",cex=0.6)
axis(side = 1)
axis(side = 2)
fig1legend <- list(x=c(100,100),y=c(0.0116031,0.0116031))
legend(fig1legend,lty=1:2,cex=0.5, bty="n",
       legend=c("normal cases","pooled, normal and special cases"))
density2 <- density(pooled_i)
lines(x = (density2$x), y = density2$y, type = "l",lty=2)

par(mfrow=c(1,3))
reldist(y=pooled_i, yo=normal_i,
               smooth=0.4, ci=FALSE,
               yolabs=seq(-1,3,by=0.5),
               ylim=c(0.5,5.0),
               bar=TRUE, quiet=FALSE,
               xlab="Proportion of Normal-Case-Distribution")
title(main=paste("Overall relative density 1993/94"))
abline(h=1,lty=2)
reldist(y=pooled_i, yo=normal_i,
               show="effect",
               bar=TRUE, quiet=FALSE,
               ylim=c(0.5,5.0), ylab="",
               smooth=0.4, ci=FALSE,
               yolabs=seq(-1,3,by=0.5),
               xlab="Proportion of Normal-Case-Distribution")
title(main=paste("Effect of Median shift"))
abline(h=1,lty=2)
reldist(y=pooled_i, yo=normal_i,
               smooth=0.4, ci=FALSE,
               show="residual",
               bar=TRUE, quiet=FALSE,
               ylim=c(0.5,5.0), ylab="",
               yolabs=seq(-1,3,by=0.5),
               xlab="Proportion of Normal-Case-Distribution")
title(main=paste("Effect of different shape"))
abline(h=1,lty=2)
par(mfrow=c(1,1))
@

1993/94 including special cases changes the distribution slightly at both ends. Special cases have a slightly lower median income and therefore are more frequent in the lower percentiles and less frequent in the upper percentiles. In addition there is an effect of shape: the distribution of special cases is more skewed so that lower percentiles show lower incomes and higher percentiles show higher incomes compared to just normal cases.

<<specialcases10, echo=FALSE,warning=FALSE>>=
library(foreign)
library(ggplot2)
#library(reldist)
normal <- filter(read.csv("../../data/ginis_und_perzentile_normal.csv",sep="\t"),kanton=="CH",steuerperiode==2010)
start <- which(names(normal)=="p1")
end <- which(names(normal)=="p99")
percentile <- c(1,5,10,20,25,30,40,50,60,70,75,80,90,95,99)
normal <- data.frame(t(normal[1,start:end]),percentile)
names(normal)[1]=c("inc")

#bruelhart data
pooled <- filter(read.csv("../../data/data_Schweiz.csv",sep=";"), Veranlagungsperiode==2010, Einheit=="Total")
start <- which(names(pooled)=="p1")
p95 <- which(names(pooled)=="p95")
end <- which(names(pooled)=="p99")
pooled <- data.frame(t(pooled[1,c(start:p95,end)]),percentile)
names(pooled)[1]=c("inc")
pooled$inc<-pooled$inc/1000 #adjust scale
normal$case <- "normal case"
pooled$case <- "pooled, normal and special cases"
percentiles <- rbind(normal,pooled)
ggplot(percentiles, aes(x=percentile,y=inc,group=case,colour=case))+
	geom_line()+theme_bw()+
	scale_colour_grey()+
	xlab("Percentile")+ylab("taxable income")+
	ggtitle("Taxable incomes of normal and special cases 2010")+
  theme(legend.justification=c(0,1),legend.position=c(0, 1))

#plot relative distribution
rel <- data.frame(pooled$inc,normal$inc,pooled$percentile)
rel$change <- rel$pooled.inc/rel$normal.inc
ggplot(rel, aes(x=pooled.percentile,y=change))+
	geom_line()+theme_bw()+
	geom_line(linetype="dashed",aes(y=1),size=2)+
	scale_colour_grey()+
	xlab("Percentile")+ylab("taxable income")+
	ggtitle("Taxable incomes of normal versus special cases 2010")

#steuerpflichtige estv / stpf bruelhart
#1- (3422210 / 3689063)

# imputing pseudo-individual data to use reldist
# we cut at the 95th percentile because it is unclear what values to use to extrapolate
ival<-na.omit(c(0,normal$inc))
perval<-c(0,normal$percentile)
normal_i<-unlist(sapply(2:length(ival),function(i){
  len=(perval[i]-perval[i-1])*100
  seq(ival[i-1],ival[i],length.out=len)
}))

#nur bis 95
ival<-na.omit(c(0,pooled$inc[-15]))
perval<-c(0,pooled$percentile)
pooled_i<-unlist(sapply(2:length(ival),function(i){
  len=(perval[i]-perval[i-1])*100
  seq(ival[i-1],ival[i],length.out=len)
}))

density1 <- density(normal_i)
plot(x = (density1$x), y = density1$y, type = "l",
     xlab = "taxable income", ylab = "density"
     #axes = FALSE,
     #xlim = c(-50, 200),
     #ylim=c(0,0.0116031)
     )
title(main="normal cases vs pooled, normal and special cases 2010",cex=0.6)
axis(side = 1)
axis(side = 2)
fig1legend <- list(x=c(120,120),y=c(0.0116031,0.0116031))
legend(fig1legend,lty=1:2,cex=0.5, bty="n",
       legend=c("normal cases","pooled, normal and special cases"))
density2 <- density(pooled_i)
lines(x = (density2$x), y = density2$y, type = "l",lty=2)

par(mfrow=c(1,3))
reldist(y=pooled_i, yo=normal_i,
               smooth=0.4, ci=FALSE,
               yolabs=seq(-1,3,by=0.5),
               ylim=c(0.5,5.0),
               bar=TRUE, quiet=FALSE,
               xlab="Proportion of Normal-Case-Distribution")
title(main=paste("Overall relative density 2010"))
abline(h=1,lty=2)
reldist(y=pooled_i, yo=normal_i,
               show="effect",
               bar=TRUE, quiet=FALSE,
               ylim=c(0.5,5.0), ylab="",
               smooth=0.4, ci=FALSE,
               yolabs=seq(-1,3,by=0.5),
               xlab="Proportion of Normal-Case-Distribution")
title(main=paste("Effect of Median shift"))
abline(h=1,lty=2)
reldist(y=pooled_i, yo=normal_i,
               smooth=0.4, ci=FALSE,
               show="residual",
               bar=TRUE, quiet=FALSE,
               ylim=c(0.5,5.0), ylab="",
               yolabs=seq(-1,3,by=0.5),
               xlab="Proportion of Normal-Case-Distribution")
title(main=paste("Effect of different shape"))
abline(h=1,lty=2)
par(mfrow=c(1,1))
@

2010 the picture is similar but more apparent: There is a small effect of median shift lowering incomes in the lowest percentiles. The effect of shape however contributes most.

@@

%As we can see from figure~\ref{fig:specialcases93942} and \ref{fig:specialcases092}, special cases differ strongly 
%from normal cases within the low and top percentiles. Within the tax period 1993/94 the fifth percentile of 
%normal cases is 15.8\% higher than the fifth percentile of the combines data while the 95\% percentile of 
%normal cases is even 0.7\% lower if one leaves out special cases. This indicates special cases are very 
%different from normal cases as the share of special cases is only 15.5\%.\footnote{1993/94 there were 2.76 
%million tax units defined as being normal cases compared to 0.51 million special cases.}
%In 2009 the situation has the same pattern. The fifth percentile of normal cases has 11\% higher taxable 
%income compared to data where special cases are included. The five percent top incomes are 4.9\% higher 
%within all cases compared to normal cases only. The share of special cases however decreased 
%to 7.2\%.\footnote{2009: 3.42 million normal cases, 0.27 million special cases}

@@

par(mfrow=c(1,3))
g10 <- reldist(y=estv2010.total.ind$inc, yo=habe10$inc_habe,
               smooth=0.4, ci=FALSE,
               yolabs=seq(-1,3,by=0.5),
               ylim=c(0.5,5.0),
               bar=TRUE, quiet=FALSE,
               xlab="Proportion of HBS Distribution")
title(main=paste("Overall relative density"))
abline(h=1,lty=2)
g1A <- reldist(y=estv2010.total.ind$inc, yo=habe10$inc_habe,
               show="effect",
               bar=TRUE, quiet=FALSE,
               ylim=c(0.5,5.0), ylab="",
               smooth=0.4, ci=FALSE,
               yolabs=seq(-1,3,by=0.5),
               xlab="Proportion of HBS Distribution")
title(main=paste("Effect of Median shift"))
abline(h=1,lty=2)
gA0 <- reldist(y=estv2010.total.ind$inc, yo=habe10$inc_habe,
               smooth=0.4, ci=FALSE,
               show="residual",
               bar=TRUE, quiet=FALSE,
               ylim=c(0.5,5.0), ylab="",
               yolabs=seq(-1,3,by=0.5),
               xlab="Proportion of HBS Distribution")
title(main=paste("Effect of different shape"))
abline(h=1,lty=2)
par(mfrow=c(1,1))

@@

par(mfrow=c(1,3))
g10 <- reldist(y=estv2010.married.ind$inc, yo=habe10.married$inc_habe,
               smooth=0.4, ci=FALSE,
               yolabs=seq(-1,3,by=0.5),
               ylim=c(0.5,5.0),
               bar=TRUE, quiet=FALSE,
               xlab="Proportion of HBS Distribution")
title(main=paste("Overall relative density"))
abline(h=1,lty=2)
g1A <- reldist(y=estv2010.married.ind$inc, yo=habe10.married$inc_habe,
               show="effect",
               bar=TRUE, quiet=FALSE,
               ylim=c(0.5,5.0), ylab="",
               smooth=0.4, ci=FALSE,
               yolabs=seq(-1,3,by=0.5),
               xlab="Proportion of HBS Distribution")
title(main=paste("Effect of Median shift"))
abline(h=1,lty=2)
gA0 <- reldist(y=estv2010.married.ind$inc, yo=habe10.married$inc_habe,
               smooth=0.4, ci=FALSE,
               show="residual",
               bar=TRUE, quiet=FALSE,
               ylim=c(0.5,5.0), ylab="",
               yolabs=seq(-1,3,by=0.5),
               xlab="Proportion of HBS Distribution")
title(main=paste("Effect of different shape"))
abline(h=1,lty=2)
par(mfrow=c(1,1))

@@

par(mfrow=c(1,3))
g10 <- reldist(y=estv2010.unmarried.ind$inc, yo=habe10.unmarried$inc_habe,
               smooth=0.4, ci=FALSE,
               yolabs=seq(-1,3,by=0.5),
               ylim=c(0.5,5.0),
               bar=TRUE, quiet=FALSE,
               xlab="Proportion of HBS Distribution")
title(main=paste("Overall relative density"))
abline(h=1,lty=2)
g1A <- reldist(y=estv2010.unmarried.ind$inc, yo=habe10.unmarried$inc_habe,
               show="effect",
               bar=TRUE, quiet=FALSE,
               ylim=c(0.5,5.0), ylab="",
               smooth=0.4, ci=FALSE,
               yolabs=seq(-1,3,by=0.5),
               xlab="Proportion of HBS Distribution")
title(main=paste("Effect of Median shift"))
abline(h=1,lty=2)
gA0 <- reldist(y=estv2010.unmarried.ind$inc, yo=habe10.unmarried$inc_habe,
               smooth=0.4, ci=FALSE,
               show="residual",
               bar=TRUE, quiet=FALSE,
               ylim=c(0.5,5.0), ylab="",
               yolabs=seq(-1,3,by=0.5),
               xlab="Proportion of HBS Distribution")
title(main=paste("Effect of different shape"))
abline(h=1,lty=2)
par(mfrow=c(1,1))
@
